Supplementary Information 1

### 2025-03-31 index.Rmd
adding mod

```{r}
SSplotTimeseries(base.model1.3,
                 subplot = 1)
SSplotTimeseries(base.model1.3,
                 subplot = 9)
SSplotTimeseries(base.model1.3,
                 subplot = 7)
```

@@

SSplotSelex(base.model1.2,
            subplots = 1)
```

```{r}
SSplotBiology(base.model1.1,
            subplots = 1:32)
```

>>>>

```{r}
SSplotTimeseries(base.model1.4,
                 subplot = 1)
SSplotTimeseries(base.model1.4,
                 subplot = 9)
SSplotTimeseries(base.model1.4,
                 subplot = 7)
```

@@

SSplotSelex(base.model1.2,
            subplots = 1)
SSplotSelex(base.model1.3,
            subplots = 1)

SSplotSelex(base.model1.4,
            subplots = 1)
```

```{r}
SSplotIndices(base.model1.1,
            subplots = 1:32)
```
